### 2011-05-05 paper/paper.tex
paper.tex

@@

>>>>

We consider the problem of randomly and uniformly sampling a point from a convex region in $n$-dimensional space. This has applications, for instance, in convex optimization \cite{Dabbene}. We phrase the problem as follows: we are given a convex region $\mathcal{R}$ in the form of a \emph{membership oracle}, a black box which can determine whether any point $x$ is in $\mathcal{R}$, along with a starting point $x_0$ in $\mathcal{R}$. The task is to sample a point from the region with with a distribution as close to uniform as possible.

Here, we study two Markov chain-based methods for sampling, the ball-walking method and the hit-and-run method and see how they perform comparitively in practice.

@@

\bibitem{Dabbene} Dabbene, F., ``A randomized cutting plane scheme for convex optimization," Computer-Aided Control Systems, 2008. CACSD 2008. IEEE International Conference on , vol., no., pp.120-125, 3-5 Sept. 2008.
